{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-26 documents/detection.tex
Wooords

>>>>

Biotium Gelgreen has a very specific advantage: to increase the safety of the dye, the flurophore is tied to some huge, unknown proprietary molecule, preventing it from diffusing through membranes or capsids. This has the side effect of making the fluorescence intensity strictly related to the quantity of genomic material dispersed in the solvent, rather than
